### 2013-02-01 doc/xps2013/proposal.tex
partial commit of research section

This interface suffers from multiple shortcomings.  Ultimately, moving data to and from a remote node requires the interaction of two different operating system processes existing on two different system nodes.  Those processes each maintain a collection of runtime data structures and moving data among them means interacting with those data structures constructively.  Often such

@@

>>>>

This interface suffers from multiple shortcomings.  The biggest of which is that ultimately, moving data to and from a remote node constructively requires higher level semantic operations than simple reads and writes.  These higher level semantics can, of course, be synthesized from the underlying read and write primitives, but it wastes round trips and synchronization time.  One possible alternative solution is to borrow ideas from Active Messages~\cite{active-messages} and enable remote nodes to dispatch, essentially, user-level function calls.  The challenge here is to make those calls interoperate securely with a modern operating system and multicore system and be efficient.  \comment{This seems weak.  Need some more ideas here.  -Mark}

The second challenge is the virtual to physical address translation on the cards requires the operating system to pin translations.  This removes paging flexibility from the operating system and allows user processes to (potentially unfairly) grab ahold of physical memory.  In the long run, the solution here likely lays at the intersection of what progress is occurring in virtual memory translation for I/O with virtual machines and RDMA.  Our goal will be carefully study the I/O virtualization proposals put forth by major processor manufactures and devise solutions that enable RDMA to capitalize on these developments.  \comment{weak?  -M}

The final challenge is that atomic operations via RDMA do not interact atomically with processors in a system.  Semantically it is not entire clear what happens if a processor issues an atomic operation on a memory address at the same time the network card is attempting to service a remote atomic access. \comment{maybe this is not true.  have to think some more about PCIe an what happens here.  might not be a problem.  -M}

@@

\subsection{Compiler and language support}
